Optimal (Multiway) Spatial Joins

### 2024-05-30 msj.tex
yufei

\extraspacing \underline{\em Proof of Statement (2).}
Suppose that $r' = [x_1,x_2] \times [y_1, y_2]$. Accordingly, $r^*$ can be written as $[x_1, x_2] \times [y_1, \maxtop(r')]$. We will first prove $\dcross_H(\bm{t})\subseteq \cross_H(r^*)$. For this purpose, given an arbitrary segment $h \in \dcross_H(\bm{t})$, we will show that $h$ crosses $r^*$. For this purpose, we need to explain why $\xleft(h) < x_1 \le x_2 < \xright(h)$ and $y_h \in [y_1, \maxtop(r')]$.
\begin{itemize}
    \item The fact $h \in \dcross_H(\bm{t})$ tells us that $h$ crosses $\gbot(\bm{t})$, which is $r'$. As the x-range of $r'$ is $[x_1,x_2]$, it must hold true that $\xleft(h) < x_1 \le x_2 < \xright(h)$.

@@

    \item The fact $h \in \dcross_H(\bm{t})$ also tells us that $h$ crosses $B_{\bm{t}}$. Hence, $y_h \in [\ybot(B_\bm{t}), \ytop(B_{\bm{t}})]$. As $r' = \gbot(\bm{t})$, we know $\ybot(B_\bm{t}) = \ybot(r') = y_1$. By the definition of $\maxtop(r')$ in \eqref{eqn:hv:type1:maxtop}, we know $\ytop(B_{\bm{t}}) \leq \maxtop(r')$. It thus follows that $y_h \in [y_1, \maxtop(r')]$.
\end{itemize}
We can now conclude that $h$ crosses $r^*$.

>>>>

\extraspacing \underline{\em Proof of Statement (2).}
Let $r', r^*$, and $\bm{t}$ be as defined in statement (2). Let us represent $r'$ as $[x_1,x_2] \times [y_1, y_2]$. Accordingly, $r^*$ can be written as $[x_1, x_2] \times [y_1, \maxtop(r')]$.

@@

We will first prove $\dcross_H(\bm{t})\subseteq \cross_H(r^*)$. For this purpose, given any segment $h \in \dcross_H(\bm{t})$, we will show that $h$ crosses $r^*$. To do so, we need to explain why $\xleft(h) < x_1 \le x_2 < \xright(h)$ and $y_h \in [y_1, \maxtop(r')]$.
\begin{itemize}
    \item The fact $h \in \dcross_H(\bm{t})$ tells us that $h$ crosses $\gbot(\bm{t})$, which is $r'$. As the x-range of $r'$ is $[x_1,x_2]$, it must hold true that $\xleft(h) < x_1 \le x_2 < \xright(h)$.

    \item The fact $h \in \dcross_H(\bm{t})$ also tells us that $h$ crosses $B_{\bm{t}}$. Hence, $y_h \in [\ybot(B_\bm{t}), \ytop(B_{\bm{t}})]$. From $r' = \gbot(\bm{t})$, we get $\ybot(B_\bm{t}) = \ybot(r') = y_1$. By the definition of $\maxtop(r')$ in \eqref{eqn:hv:type1:maxtop}, we know $\ytop(B_{\bm{t}}) \leq \maxtop(r')$. It thus follows that $y_h \in [y_1, \maxtop(r')]$.
\end{itemize}
We can now conclude that $h$ crosses $r^*$.
